Classless Java

### 2015-10-15 paper/sections/Formalization.tex

\begin{figure}[h]
\begin{grammar}
\production{
\e
}{
  \x\mid\MCall\e\m\es\mid\MCall{\C}\m\es\mid\MCall{\C\QM{.super}}\m\es\mid\obj
  }{expressions}\\
\production{
\obj
}{
\QM{new}\ \C\oR\cR\oC\T_1\ \f_1\QM;\ldots\T_k\ \f_k\QM;\
\mh_1\oC\QM{return}\ \e_1\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_n\QM{;}\!\cC
\cC
  }{object creation}\\
\production{
\metaVar{I}
}{
 \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_k \oC\method_1\ldots\method_n\cC
  }{interface declaration}\\
\production{
\method
}{
 \QM{static}\ \mh\ \oC\QM{return}\ \e\QM{;}\!\cC
\mid
\QM{default}\ \mh\oC\QM{return}\ \e\QM{;}\cC
\mid
\mh\QM{;}
  }{method declaration}\\
\production{
\mh
}{
 \T_0\ \m\ \oR\T_1\ \x_1\ldots\T_n\ \x_n\cR
  }{method header}\\
\production{
\ann
}{
  \mixinAnn|\emptyset
  }{annotations}\\
\end{grammar}
\caption{Grammar of ClassLess Java}
\label{Grammar}
\end{figure}

@@

\[ \inferrule{
  \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{
  \methods \} \text{ OK }}
{ \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods \} \longmapsto \\
  \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods; \textsf{ofMethod}(C_0); \textsf{otherMethod}(C_0) \}
} \quad \textsc{(Translation)} \]

@@

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=5in]{screenshot.png}
\caption{Screenshot.}\label{screenshot_png}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=5in]{table.png}
\caption{Table.}\label{table_png}
\end{figure}

\haoyuan{
I found this from the Internet. See Fig.~\ref{screenshot_png}.
An experiment. See Fig.~\ref{table_png}.
}

@@

\begin{equation*}
\begin{array}{ll}
\textsf{ofMethod}(C_0) = ... & ... \\
\textsf{otherMethod}(C_0) = \methods_1; \methods_2 \hspace{0.1in} & \mif\ \textsf{resolve}(C_0) = \overline{field} \\
& \method_1 = \textsf{with}(field, C_0) \\
& \method_2 = \textsf{clone}(field, C_0) \\
\textsf{resolve}(C_0) = \overline{field} & \mif\ \textsf{methods}(C_0) = \mhs \\
& \forall \mh \in \mhs, \mh \textsf{ isField or isWith or isClone or isDefault} \\
& \forall field \in \overline{field},\ \mh^{field} = T\ m\oR\cR,\ \mif\ \mBody(m, C_0) = T\ m\oR\cR\QM; \\
\textsf{methods}(C_0) = \mhs\ \bigcup\ \overline{\textsf{methods}(C)} & \mif\ \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \} \\
& \method\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \} \\
\textsf{with}(field, C_0) = T_0\ \QM{with}m\oR T\ x\cR\QM; & \mif\ \mh^{field} = T\ m\oR\cR,\ \mh' = T'\ \QM{with}m\oR T\ x\cR \\
& \mBody(\QM{with}m, C_0) \in \{ \mh'\QM;, \QM{default}\ \mh' \mbox{\Q@\{return \_;\}@}\} \\
& IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \},\ T_0 <: T' \\
\textsf{clone}(field, C_0) = T_0\ \QM{clone}\oR\cR\QM; & \mif\ IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \}
\end{array}
\end{equation*}

\haoyuan{``\textsf{isField or isWith or isClone or isDefault}''?}

>>>>

\begin{figure}[h]
\begin{grammar}
\production{
\e
}{
  \x\mid\MCall\e\m\es\mid\MCall{\C}\m\es\mid\MCall{\C\QM{.super}}\m\es\mid\obj
  }{expressions}\\
\production{
\obj
}{
\QM{new}\ \C\oR\cR\oC\T_1\ \f_1 = e_1\QM;\ldots\T_k\ \f_k = e_k\QM;\
\mh_1\oC\QM{return}\ \e_{k+1}\QM{;}\!\cC
\ldots
\mh_n\oC\QM{return}\ \e_{k+n}\QM{;}\!\cC
\cC
  }{object creation}\\
\production{
\metaVar{I}
}{
 \ann\ \QM{interface}\ \C_0\ \QM{extends}\ \C_1\ldots\C_k \oC\method_1\ldots\method_n\cC
  }{interface declaration}\\
\production{
\method
}{
 \QM{static}\ \mh\ \oC\QM{return}\ \e\QM{;}\!\cC
\mid
\QM{default}\ \mh\oC\QM{return}\ \e\QM{;}\cC
\mid
\mh\QM{;}
  }{method declaration}\\
\production{
\mh
}{
 \T_0\ \m\ \oR\T_1\ \x_1\ldots\T_n\ \x_n\cR
  }{method header}\\
\production{
\ann
}{
  \mixinAnn|\emptyset
  }{annotations}\\
\end{grammar}
\caption{Grammar of ClassLess Java}
\label{Grammar}
\end{figure}

@@

\[ \inferrule{
  \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{
  \methods \} \text{ OK }}
{ \Gamma \vdash \mixinAnn \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods \} \longmapsto \\
  \emptyset \text{ interface } C_0 \text{ extends } \overline{C} \{ \methods; \textsf{ofMethod}(C_0); \textsf{otherMethod}(C_0) \}
} \quad \textsc{(Translation)} \]

@@

\textbf{THEOREM. } If $I \longmapsto I'$ and $I$ OK, then $I'$ OK.

@@

\begin{comment}
\begin{figure}[tbp]
\centering
\includegraphics[width=5in]{screenshot.png}
\caption{Screenshot.}\label{screenshot_png}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=5in]{table.png}
\caption{Table.}\label{table_png}
\end{figure}
\end{comment}

@@

\begin{equation*}
\begin{array}{ll}
\textsf{ofMethod}(C_0) = \QM{static of} \oR T_1\ m_1\QM,\ldots T_k\ m_k\cR\ \QM{\{} &  \\
\ \ \ \ \QM{return new}\ C_0 \oR\cR\ \QM{\{}  & \mif\ \textsf{resolve}(C_0) = \overline{field} \\
\ \ \ \ \ \ \ \ T_1\ \_m_1 = m_1\QM;\ldots T_k\ \_m_k = m_k\QM; & \forall field_i \in \overline{field},\ \mh^{field_i} = T_i\ m_i\oR\cR \\
\ \ \ \ \ \ \ \ T_i\ m_i\oR\cR\ \QM{\{return}\ \_m_i\QM{;\}}\ \ldots & T_i\ m_i\oR\cR \textsf{ included for all } i \\
\ \ \ \ \ \ \ \ T_0\ \QM{with}m_i\oR T_i\ x_i\cR\ \QM{\{} & T_0\ \QM{with}m_i\oR T_i\ x_i\cR \textsf{ included if with}(field_i, C_0) \textsf{ defined} \\
\ \ \ \ \ \ \ \ \ \ \ \ \QM{return this.of}\oR m_1\oR\cR\QM,\ldots x_i\QM,\ldots m_k\oR\cR\cR\QM{;} & \\
\ \ \ \ \ \ \ \ \QM{\}}\ \ldots & \\
\ \ \ \ \ \ \ \ T_0\ \QM{clone}\oR\cR\ \QM{\{} & \\
\ \ \ \ \ \ \ \ \ \ \ \ \QM{return this.of}\oR m_1\oR\cR\QM,\ldots m_k\oR\cR \cR\QM; & \\
\ \ \ \ \ \ \ \ \QM{\}} & \\
\ \ \ \ \QM{\};} & \\
\QM{\}} & \\
\textsf{otherMethod}(C_0) = \methods_1; \methods_2 \hspace{0.1in} & \mif\ \textsf{resolve}(C_0) = \overline{field} \\
& \method_1 = \textsf{with}(field, C_0) \\
& \method_2 = \textsf{clone}(field, C_0) \\
\textsf{resolve}(C_0) = \overline{field} & \mif\ \textsf{methods}(C_0) = \methods \\
& \forall \method \in \methods, \method \textsf{ isField or isWith or isClone or isDefault} \\
& \forall field \in \overline{field},\ \mh^{field} = T\ m\oR\cR \\
& \ \ \ \ \mif\ \mBody(m, C_0) = T\ m\oR\cR\QM;\ m\ne\QM{clone} \\
\textsf{methods}(C_0) = \overline{meth'}\ \bigcup\ \overline{\textsf{methods}(C)} & \mif\ \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \} \\
& \method'\in\{\mh\QM;,\QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \} \\
\textsf{with}(field, C_0) = T_0\ \QM{with}m\oR T\ x\cR\QM; & \mif\ \mh^{field} = T\ m\oR\cR,\ \mh' = T'\ \QM{with}m\oR T\ x\cR \\
& \mBody(\QM{with}m, C_0) \in \{ \mh'\QM;, \QM{default}\ \mh' \mbox{\Q@\{return \_;\}@}\} \\
& IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \},\ T_0 <: T' \\
\textsf{clone}(field, C_0) = T_0\ \QM{clone}\oR\cR\QM; & \mif\ IT(T_0) = \text{\emph{ann} interface } C_0 \text{ extends } \overline{C} \{ \methods \} \\
\method \textsf{ isField} & \mif\ \method = T\ m\oR\cR\QM;\ m\ne\QM{clone} \\
\method \textsf{ isWith} & \mif \\
\method \textsf{ isClone} & \mif\ \method = T\ \QM{clone}\oR\cR\QM; \\
\method \textsf{ isDefault} & \mif\ \method = \QM{default}\ \mh\mbox{\Q@\{return \_;\}@} \\
\end{array}
\end{equation*}
